Applying automated verification to optimal sizing of stand-alone solar photovoltaic systems\\

### 2019-04-22 Tex/ASE2019/Conference-LaTeX-template_7-9-18/Trindade_ASE2019_optimization PV systems_rev0.tex
updated text ASE

The sizing check will be performed by the proposed tool, and this stage ensures that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho}. 
%
Firstly, it is needed to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho}.
\begin{equation}
\label{eq:Ecorrected}
\scriptstyle E_{corrected} = \dfrac{\scriptstyle E_{consumption}}{ \scriptstyle \eta_{b} \eta_{c} \eta_{i} }.
\end{equation}

@@

\section{Results and Discussion}
We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}. Furthermore, four start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (CBMC, ESBMC, UAutomizer, and CPAchecker), were used to compare the approach effectiveness and efficiency. The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}.

\begin{table}
\caption{Case studies and Results: optimization of PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|}
\hline
\hline
 & Case 1 & Case 2\\
\hline
\hline
Tool & \makecell{Demand = 501W \\ Peak = 501W \\ Energy=3900Wh/day} & \makecell{Demand = 915W \\ Peak = 980W \\ Energy=4880Wh/day}\\
\hline
CBMC 5.11 (MiniSat 2.2.1) & x1 & x2 \\
\hline
ESBMC 6.0.0 (Boolector 3.0.1) & x1 & x2 \\
\hline
UAutomizer 0.1.24 (Z3 4.8.3) & x1 & x2 \\
\hline
CPAchecker 1.8 (MathSAT 5.5.3) & x2 & x4 \\
\hline
\hline
\end{tabular}
\end{scriptsize}
\end{table}

>>>>

The sizing check will be performed by the proposed tool, and this stage ensures that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (maximum power point tracking) charge controller, that is the most common nowadays. 
%
Firstly, it is needed to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho}.
\begin{equation}
\label{eq:Ecorrected}
\scriptstyle E_{corrected} = \dfrac{\scriptstyle E_{consumption}}{ \scriptstyle \eta_{b} \eta_{c} \eta_{i} }.
\end{equation}

@@

\section{Results and Discussion}
We have performed two case studies to evaluate the proposed approach of optimization as described in Table~\ref{tab1}. Furthermore, four start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification}: CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector}, UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used to compare the approach effectiveness and efficiency. The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}.

All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. The experiments were performed with a predefined timeout of 240 minutes.

%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
\begin{table}
\caption{Case studies and Results: optimization of PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|}
\hline
\hline
 & Case 1 & Case 2\\
\hline
\hline
Tool & \makecell{Demand = 501W \\ Peak = 501W \\ Energy=3900Wh/day \\ Battery autonomy=48h} & \makecell{Demand = 915W \\ Peak = 980W \\ Energy=4880Wh/day \\ Battery autonomy=6h}\\
\hline
CBMC 5.11 (MiniSat 2.2.1) & Out of Memory & Out of Memory \\
\hline
ESBMC 6.0.0 (Boolector 3.0.1) & Timeout & Timeout \\
\hline
UAutomizer 0.1.24 (Z3 4.8.3) & UNKNOWN & UNKNOWN \\
\hline
CPAchecker 1.8 (MathSAT 5.5.3) & SAT (65 minutes) & x4 \\
\hline
\hline
\end{tabular}
\end{scriptsize}
\end{table}
